High-Dim Project

### 2014-12-18 highdim-paper/paper.tex
figure
updated lambda-accuracy plot

\documentclass[11pt]{article}
\usepackage{acl2014}
\usepackage{times}
\usepackage{url}
\usepackage{latexsym}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage[]{algorithm2e}

@@

In section 2, we will provide some background on latent group lasso and 
multiclass classification. Latent group Lasso is based on applying the usual 
group Lasso penalty on a set of latent variables when groups are overlapping.
In section 3, we will present our model, which uses hinge loss for training classifiers. 
The following sections will include detailed explanations of our datasets and the 
results we gathered.

@@

\begin{figure}[ht]
\begin{center}
	\includegraphics[width=5cm, natwidth=200, natheight=206]{m_img}
	\caption{Group-wise sparse weight matrix generated: 5 classes, 25 features in 5 groups}
\end{center}
\end{figure}

@@

\begin{figure}[ht]
\begin{center}
	\includegraphics[width=5cm, natwidth=200, natheight=307]{m1_img}
	\caption{Target group-wise sparse weight matrix generated: 5 classes, 25 features in 5 groups}
\end{center}
\end{figure}

\begin{figure}[ht]
\begin{center}
	\includegraphics[width=8cm,natwidth=200, natheight=186]{m2_img}
	\caption{Weight matrix calculated from the training data. It's similar to the one generated.}
\end{center}
\end{figure}

@@

Accuracy. In our experiments, the generator algorithm was configured to produce 150 random vectors from the underlying model where it consists of 5 classes and 25 features in 5 groups. The accuracy achieved was about $60\%$ to $70\%$. \\

>>>>

\documentclass[11pt]{article}
\usepackage{acl2014}
\usepackage{times}
\usepackage{url}
\usepackage{latexsym}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage[]{algorithm2e}
\usepackage{caption}
\usepackage{subcaption}

@@

In section 2, we will provide some background on latent group lasso and 
multiclass classification. Latent group Lasso is based on applying the usual 
group Lasso penalty on a set of latent variables when groups are overlapping.
In section 3, we will present our model, which uses hinge loss for training classifiers. 
The latter sections will include detailed explanations of our datasets and the 
results we gathered.

@@

\begin{figure}[ht]
\begin{center}
	\includegraphics[width=.5\linewidth]{m_img}
	\caption{Group-wise sparse weight matrix generated: 5 classes, 25 features in 5 groups}
\end{center}
\end{figure}

@@

\begin{figure}[ht]
  \centering
  \includegraphics[width=.5\linewidth]{m1_img}
  \caption{Target group-wise sparse weight matrix generated: 5 classes, 25 features in 5 groups}
\end{figure}%

\begin{figure}[ht]
  \centering
  \includegraphics[width=.9\linewidth]{m2_img}
  \caption{Weight matrix calculated from the training data. It's similar to the one generated.}
\end{figure}

@@

Accuracy. In our experiments, the generator algorithm was configured to produce 150 random vectors from the underlying model where it consists of 5 classes and 25 features in 5 groups. The accuracy achieved is closely related to the L2-norm regularization constant $\lambda$. The following figure shows the relation between lambda-accuracy and lambda-density.\\

\begin{figure}[ht]
\begin{center}
	\includegraphics[width=\linewidth]{m3_img}
	\caption{lambda-accuracy and lambda-density plot (150 samples, 5 classes, 25 features in 5 groups)}
\end{center}
\end{figure}
